Which ``Bad Smells'' Can Be Ignored?

### 2016-03-13 Manuscript.tex
Updates from ShareLaTeX

{\em PROBLEM \#4:} It is hard to judge the  effects of removing bad smells.
Refactored code cannot be assessed just by a rerun of the the test
suite since (refactorings are supposed to preserve behavior), and otherwise one must wait for new defect reports to evaluate the effect of refactoring changes on code.  
% waiting to observe 
% code refactorings is meant to
% preserve the behavior of the system (i.e. the same tests
% should pass before and after the refactoring). 
% Also, it many not be practical
%  to assessing refactorings by making the
% refactorings,  then seeing what happens to that code for the rest
% of the project. In a test-driven agile project, as
% SCRUM meetings change what stories are implemented next,
% the operational profile that lead to defects in the old
% code may not be repeated in future executions. 
To resolve this  problem, SE researchers such as 
Cheng et al.~\cite{Cheng10}, O'Keefe et al.~\cite{OKeeffe08,OKeeffe07},
Moghadam~\cite{Moghadam2011} and Mkaouer et al.~\cite{Mkaouer14}
use a pair of systems: 
\begin{enumerate}
    \item One system to propose changes;
\item A separate system to assess
how defective is the code before and after some
refactoring.
\end{enumerate}
For the second system,
 Cheng, O'Keefe, Moghadam and  Mkaouer et al. use the QMOOD hierarchical
quality model~\cite{Bansiya02}.
A shortcoming of QMOOD
is that quality models learned from other projects
may perform poorly when applied to new projects~\cite{localvsglobal}.

@@

VARL encodes the defect count
for each class as 0 (no defects known in class) or 1 (defects known in class).
Univariate binary logistic regression is applied to learn three coefficients:  
 $\alpha$ is the intercept constant;
    $\beta$ is the coefficient for maximizing log-likelihood;
  and $p_0$  
    measures   how well this   model predicts for   defects.
Any code metric with $p_0>0.05$ is  rejected as being a poor defect predictor. Thresholds are then learned from the surviving metrics $M_c$ using
an equation proposed by Bender:
\begin{equation}
 \mathit{bad\; smell\; if\;} M_c > \frac{1}{\beta }\left( {\log \left( {\frac{{{p_1}}}{{1 - {p_1}}}} \right) - \alpha } \right) 
\end{equation}
For consistency
with Shatnawi, we explore the correlation between
the code metrics and the defect counts and   reject code metrics that are poor predictors of defects (i.e.   those  with $p > 0.05$).
\subsubsection{ Alves et al.}
Alves et al.~\cite{Alves2010} propose another approach
to finding thresholds that  utilizes the underlying statistical distribution and scale of the metrics. 
Metric values for each class are weighted according to the source lines of code (SLOC) of the class. All the weighted metrics are then normalized by the sum of all weights of for the system. 
The normalized metric values are ordered in an ascending fashion (this is equivalent to computing a density function, in which the x-axis represents the weight ratio (0-100\%), and the y-axis the metric scale).
Alves et al. then select a percentage value (they suggest 90\%) which represents the ``normal'' values for metrics. The metric threshold, then, is the metric value for which 90\% of the classes fall below. The intuition  is that the worst code has outliers beyond 90\% of the normal code measurements. Hermans et al.~\cite{hermans15} used the
Alves et al. method in their  2015 paper on
exploring bad smells.

@@

We use 40 repeated runs, each with different random number seeds (we use 40 since that is  more than the 30 samples  needed to satisfy the central limit theorem). Each run collects the \eq{diff} values.
We use multiple runs since two of our methods use some random choices: CD uses the  stochastic WHERE clustering algorithm~\cite{Menzies2013:local}
while XTREE non-deterministically picks thresholds randomly from
the high and low boundary of a range. 
 Hence, to compare all
four methods, we must run the analysis many times.

@@

In implement Scott-Knott using our data,
  we
sorted a list of  $l=40$ values of \eq{diff} values found in  $ls=4$ different methods. 
Then, we split $l$ into sub-lists $m,n$ in order to maximize the expected value of differences in the observed performances before and after divisions. E.g. for lists $l,m,n$ of size $ls,ms,ns$ where $l=m\cup n$: \[E(\Delta)=\frac{ms}{ls}abs(m.\mu - l.\mu)^2 + \frac{ns}{ls}abs(n.\mu - l.\mu)^2\]
We then apply a apply a statistical hypothesis test $H$ to check
if $m,n$ are significantly different  (in our case, the conjunction of A12 and bootstrapping). If so, Scott-Knott recurses on the splits. In other words, we divide the data if \textit{both} bootstrap sampling and effect size test agree that a division is statistically significant (with a confidence of 99\%) and not a small effect ($A12 \ge 0.6$).
For a justification of the use of non-parametric bootstrapping, see Efron \& Tibshirani~\cite[p220-223]{efron93}. For a justification of the use of effect size tests see Shepperd\&MacDonell~\cite{shepperd12a}; Kampenes~\cite{kampenes07}; and Kocaguenli et al.~\cite{Kocaguneli2013:ep}. These researchers warn that even if a hypothesis test declares two populations to be ``significantly'' different, then that result is misleading if the ``effect size'' is very small. Hence, to assess the performance differences we first must rule out small effects using A12, a test   recently endorsed by Arcuri and Briand at ICSE'11~\cite{arcuri11}.

@@

\input{tex/rq2.tex}
\newpage
\subsection{Results}

@@

\section{Conclusions}
Which  bad smells be ignored? 
We say: ignore those not supported by the historical log of data from
the current project.

@@

In accordance to that test, using the median values of each method, we
sort a list of  $l=40$ values of $R$ values found in  $ls=4$ different methods. 
Then, we split $l$ into sub-lists $m,n$ in order to maximize the expected value of differences  in the observed performances before and after divisions. E.g. for lists $l,m,n$ of size $ls,ms,ns$ where $l=m\cup n$: \[E(\Delta)=\frac{ms}{ls}abs(m.\mu - l.\mu)^2 + \frac{ns}{ls}abs(n.\mu - l.\mu)^2\]

>>>>

{\em PROBLEM \#4:} It is hard to judge the  effects of removing bad smells.
Refactored code cannot be assessed just by a rerun of the the test
suite (since refactorings are supposed to preserve behavior), and otherwise one must wait for new defect reports to evaluate the effect of refactoring changes on code.  
% waiting to observe 
% code refactorings is meant to
% preserve the behavior of the system (i.e. the same tests
% should pass before and after the refactoring). 
% Also, it many not be practical
%  to assessing refactorings by making the
% refactorings,  then seeing what happens to that code for the rest
% of the project. In a test-driven agile project, as
% SCRUM meetings change what stories are implemented next,
% the operational profile that lead to defects in the old
% code may not be repeated in future executions. 
To resolve this  problem, SE researchers such as 
Cheng et al.~\cite{Cheng10}, O'Keefe et al.~\cite{OKeeffe08,OKeeffe07},
Moghadam~\cite{Moghadam2011} and Mkaouer et al.~\cite{Mkaouer14}
use a pair of systems: 
\begin{enumerate}
    \item One system to propose changes;
\item A separate system to assess
how defective is the code before and after some
refactoring.
\end{enumerate}
For the second system,
 Cheng, O'Keefe, Moghadam and  Mkaouer et al. use the QMOOD hierarchical
quality model~\cite{Bansiya02}.
A shortcoming of QMOOD
is that quality models learned from other projects
may perform poorly when applied to new projects~\cite{localvsglobal}.

@@

VARL encodes the defect count
for each class as 0 (no defects known in class) or 1 (defects known in class).
Univariate binary logistic regression is applied to learn three coefficients:  
 $\alpha$ is the intercept constant;
    $\beta$ is the coefficient for maximizing log-likelihood;
  and $p_0$  
    measures   how well this   model predicts for   defects.
Any code metric with $p_0>0.05$ is  rejected as being a poor defect predictor. Thresholds are then learned from the surviving metrics $M_c$ using
an equation proposed by Bender:
\begin{equation}
 \mathit{bad\; smell\; if\;} M_c > \frac{1}{\beta }\left( {\log \left( {\frac{{{p_1}}}{{1 - {p_1}}}} \right) - \alpha } \right) 
\end{equation}

\newpage
\subsubsection{ Alves et al.}
Alves et al.~\cite{Alves2010} propose another approach
to finding thresholds that  utilizes the underlying statistical distribution and scale of the metrics. 
Metric values for each class are weighted according to the source lines of code (SLOC) of the class. All the weighted metrics are then normalized by the sum of all weights of for the system. 
The normalized metric values are ordered in an ascending fashion (this is equivalent to computing a density function, in which the x-axis represents the weight ratio (0-100\%), and the y-axis the metric scale).
Alves et al. then select a percentage value (they suggest 90\%) which represents the ``normal'' values for metrics. The metric threshold, then, is the metric value for which 90\% of the classes fall below. The intuition  is that the worst code has outliers beyond 90\% of the normal code measurements. Hermans et al.~\cite{hermans15} used the
Alves et al. method in their  2015 paper on
exploring bad smells.

For consistency
with Shatnawi, we explore the correlation between
the code metrics and the defect counts and   reject code metrics that are poor predictors of defects (i.e.   those  with $p > 0.05$).

@@

We use 40 repeated runs, each with different random number seeds (we use 40 since that is  more than the 30 samples  needed to satisfy the central limit theorem). Each run collects the \eq{diff} values.
We use multiple runs since two of our methods use some random choices: CD uses the  stochastic WHERE clustering algorithm~\cite{localvsglobal}
while XTREE non-deterministically picks thresholds randomly from
the high and low boundary of a range. 
 Hence, to compare all
four methods, we must run the analysis many times.

@@

To  apply Scott-Knott,
  we
sorted a list of  $l=40$ values of \eq{diff} values found in  $ls=4$ different methods. 
Then, we split $l$ into sub-lists $m,n$ in order to maximize the expected value of differences in the observed performances before and after divisions. E.g. for lists $l,m,n$ of size $ls,ms,ns$ where $l=m\cup n$: \[E(\Delta)=\frac{ms}{ls}abs(m.\mu - l.\mu)^2 + \frac{ns}{ls}abs(n.\mu - l.\mu)^2\]
We then apply a apply a statistical hypothesis test $H$ to check
if $m,n$ are significantly different  (in our case, the conjunction of A12 and bootstrapping). If so, Scott-Knott recurses on the splits. In other words, we divide the data if \textit{both} bootstrap sampling and effect size test agree that a division is statistically significant (with a confidence of 99\%) and not a small effect ($A12 \ge 0.6$).
For a justification of the use of non-parametric bootstrapping, see Efron \& Tibshirani~\cite[p220-223]{efron93}. For a justification of the use of effect size tests see Shepperd\&MacDonell~\cite{shepperd12a}; Kampenes~\cite{kampenes07}; and Kocaguenli et al.~\cite{Kocaguneli2013:ep}. These researchers warn that even if a hypothesis test declares two populations to be ``significantly'' different, then that result is misleading if the ``effect size'' is very small. Hence, to assess the performance differences we first must rule out small effects using A12, a test   recently endorsed by Arcuri and Briand at ICSE'11~\cite{arcuri11}.

@@

\input{tex/rq2.tex}

\subsection{Results}

@@

\section{Conclusions}
Which  bad smells can  be ignored? 
We say: ignore those not supported by the historical log of data from
the current project.

@@

In accordance to that test,  we
sort a list of  $l=40$ values of $R$ values found in  $ls=4$ different methods. 
Then, we split $l$ into sub-lists $m,n$ as to maximize the expected value of differences  in   observed performances before and after divisions. E.g. for lists $l,m,n$ of size $ls,ms,ns$ where $l=m\cup n$: \[E(\Delta)=\frac{ms}{ls}abs(m.\mu - l.\mu)^2 + \frac{ns}{ls}abs(n.\mu - l.\mu)^2\]
